Adversarial Training of Invariant Features for Speech Recognition

### 2017-03-21 interspeech/paper.tex
Return Phil's changes

\section{Background}
\label{sec:background}
\emph{Generative Adversarial Networks} consist of two networks: the generator and the discriminator. 
    The generator network $G$ has an
    input of randomly-generated feature vectors $\bm{z}$ and is asked to produce a
    sample $\bm{x}$, e.g.\ an image, similar to the images in the training set. The discriminator network $D$
    can either receive a generated image from the generator $G$ or an image
    from the training set. Its task is to distinguish
    between the ``counterfeit'' generated image and the ``genuine'' image taken from the dataset. Thus,
    the discriminator is just a classifier network with a sigmoid output layer
    and can be trained with gradient back-propagation. This gradient can be propagated further
    to the generator network (assuming that the output of the generator is
    continuous).

>>>>

\section{Background}
\label{sec:background}
\emph{Generative Adversarial Networks} are data generating neural networks that
    have been especially successful at producing small images.
    Unlike most generative models, they are not trained by optimizing the
    likelihood of the data, but by the optimization of a so-called
    \emph{adversarial} objective. The training of Generative Adversarial
    Networks, involves two neural networks: the generator and the discriminator.

    The generator network $G$ has an
    input of randomly-generated feature vectors $\bm{z}$ and is asked to produce a
    sample $\bm{x}$, e.g.\ an image, similar to the images in the training set. The discriminator network $D$
    can either receive a generated image from the generator $G$ or an image
    from the training set. Its task is to distinguish
    between the ``counterfeit'' generated image and the ``genuine'' image taken from the dataset. Thus,
    the discriminator is just a classifier network with a sigmoid output layer
    and can be trained with gradient back-propagation. This gradient can be propagated further
    to the generator network (assuming that the output of the generator is
    continuous).
